\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\begin{document}

\header{eric}{perlinski}{IT engineer \\ 5 rue de la libération, RONCOURT, 57860, France \\ +33 6 25 20 37 34 / eric.perlinski@clearstream.com} % Your name and current job title/field
%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

%\begin{aside} % In the aside, each new line forces a line break
%\section{contact}
%19 rue du général de Castelnau
%Villers-Lès-Nancy, 54600
%France
%~
%+33 6 25 20 37 34
%~
%\href{mailto:eric.perlinski@telecomnancy.net}{eric.perlinski@gmail.com}
%\section{languages}
%French mother tongue
%English (Toeic : 875)
%A little German \& Japanese
%\section{programming}
%C, C++, C\#
%Java, Python, PHP
%Assembly, ADA 95
%\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{\\ 2016--2013}
{Computer Engineering Degree}
{Telecom Nancy, Villers-Lès-Nancy, France}
{\\Specialized in Software Development, equivalent to or better than a Master's Degree in Computer Science. \\ \\ \textit{\textbf{IT Lectures followed : }} \\ 
Safe system’s design, Distributed systems and application, Artificial Intelligence, Software Engineering, Advanced Software Engineering, Advanced Databases, Object Oriented Programming, Parallel Algorithms, Web development, Advanced Systems \&  Networks, Compiler's creation, Digital Image processing. \\ \\ \textit{\textbf{Non-IT Lectures followed : }} \\ 
Mathematics, Statistics, Accounting, Finance, Law, Project Management, QA Management, Production Management
}


%------------------------------------------------

\entry
{\\2013--2011}
{Computer Science DUT}
{University of Lorraine, Metz, France}
{\\Granted after 2 years in Higher Education \\ \\
I studied computer science basics such as software development, networking, databases, Compilation, Objected Oriented Programming and Shell scripting.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\subsection{Software Engineer at LOGOS IT Services}

\begin{entrylist}
\entry
{\\Oct. 2016--Today}
{Clearstream Services S.A.}
{Kirchberg, Luxembourg}
{\\ \emph{IT Consultant (C++, Perl, Oracle DBMS, PL/SQL)} \\ \\
As part of the Custody back-end development team, I work on the different Clearstream's Custody back-end applications such as Custody, Custody\_TI and NASA. My work consists in adapting the behaviour of these applications to new requirements. In that purpose, I carry out C++ developments using the various tools and frameworks that are available such as the Ti framework. Due to the fact that Clearstream's applications are using Oracle are a database managment system, I also carry out SQL and PL/SQL development. I also do Perl and Shell scripts development in order to implement unit tests and regression tests to ensure that the development that has been done is correct but I also fix the different problems that can appear during technical and business acceptance tests phases.  \\ \\
\textit{\textbf{Work environment}}\\
C++, C, Perl, Shell scripting (ksh, sh), Oracle DBMS, Oracle Advanced Queuing, Ti / Oxi Framework, RHEL}


\end{entrylist}

\subsection{Internships}

\begin{entrylist}

%------------------------------------------------
\entry 
{2016 (6 months)}
{LOGOS IT Services}
{Alzingen, Luxembourg}
{\\ \emph{Software engineer intern (Java, JEE, GWT)} \\ \\
As part of my graduation internship, I worked on the development and the maintenance of LOGOS's ERP. This ERP is used to collect, store and manage data from business activities. All data were stored in the same database scheme resulting in possible security issues. I had to find a way to fix these issues by splitting the database scheme and splitting the ERP. The work done consisted in following all the different steps that could be find in a V cycle, which means bug-fixing, writing specifications, design and development of a solution. It also consisted in deploying the proposed solution in tests and production environment and providing support to the end users.\\
\\ \textit{\textbf{Work environment }} \\ 
Eclipse, Windows Linux, Java/JEE, Tomcat 7, MySQL 5.7 / SQL, GWT / Sencha 
GXT, Guice, JPA / Hibernate, HTML / XML / CSS, Jenkins, Nexus, Maven, JIRA}

\entry
{\\2015 (2 months)}
{Starburst Computing}
{Loria Laboratory, Vandoeuvre-Lès-Nancy}
{\\ \emph{IT intern (C++,Unreal Engine 4)} \\ \\
During my second year internship, I was part of the Starburst Computing team. They worked on a way to mutualize capabilities of devices connected through local area network. In order to illustrate the concept, they wanted to link two different devices through a video game that is running on two different game engines. I created a C++ adapter between Starburst Engine and a video game engine. Also, I managed to create a complete video game using Unreal Engine (Artificial Intelligence, level design, gameplay features and sound design) that uses the C++ adapter.  
}

%------------------------------------------------

\end{entrylist}

\subsection{Interdisciplinary Research project}

\begin{entrylist}

\entry
{2015}
{Loria Laboratory}
{Vandoeuvre-Lès-Nancy, France\\}
{ \emph {IT developer (C, C++, C\#, Unity3D)}\\
The project was part of a research work on distributed artificial intelligence calculations. I managed to create a client-server application in C++ that interacted with a C\# video game engine by using ZeroMQ as a middleware. The aim was to do pathfinding calculations outside of the game engine. I also created a complete demo in order to have a proof of concept. }

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{entrylist}
\entry
{ }
{IT Skills}
{ }
{ C++, C, Perl, Shell Scripts, SQL, PL/SQL, Oracle databases, OAQ, Mysql, Git / Mercurial / Clearcase / Svn, Jenkins, Nexus, Maven, C\#, Java / JEE,  ZeroMQ, RabbitMQ, Python, PHP, JavaScript, JQuery, (x)HTML \& CSS, RHEL, Debian GNU/Linux, Windows, Apache, Tomcat, IIS }
\entry
{ }
{Languages}
{ }
{French mother tongue, English (Toeic : 875), A little German \& Japanese}
\end{entrylist}
\section{Interests}

\textbf{professional:} Programming, Software design \& engineering, Artificial Intelligence, Distributed calculation \\
\textbf{personal:} Programming, News, Music, Movies, Video games, Japanese Animation


%----------------------------------------------------------------------------------------

\end{document}